

---
title: "meta_analysis"
author: "Theodore Rogers, Olivia Costa, Quincey Feragen, Penelope Corbett"
date: "2023-11-21"
output:
  html_document: default
  pdf_document: default
---
reading excel spreadsheet
```{r}
library(readxl)
big_data = read_excel("/Users/olivia/Downloads/meta_analysisDat.xlsx")
# do one test on all of the models in table 4
# add study location as predictor
# you don't have to do analyses on specifically one location or another
```
creating dataframe of numerics as default
```{r}
dat = cbind.data.frame(big_data$dataSet)
# creating dataframe of numerics as default
suppressWarnings({
for (col in big_data[2:28]) {
  dat = cbind.data.frame(dat, as.numeric(col))
}  })
colnames(dat) <- names(big_data)
full_data_vals <- dat
```
changing specific values to their specific things for full_data_names (not income, due to currency differences)
```{r}
library(dplyr)
#ladder
ladder <- as.factor(dat$ladder)
dat$ladder <- ladder

# columns 3 to 8
for (i in 3:8) {
  dat[i][dat[i] == "1"] <- "yes"
  dat[i][dat[i] == "2"] <- "no"
}
# columns 11 to 16
for (i in 11:16) {
  dat[i][dat[i] == "1"] <- "yes"
  dat[i][dat[i] == "2"] <- "no"
}
  
# columns 19 to 23
for (i in 19:23) {
  dat[i][dat[i] == "1"] <- "yes"
  dat[i][dat[i] == "2"] <- "no"
}
  
# gender
dat$gender[dat$gender == "1"] <- "woman"
dat$gender[dat$gender == "2"] <- "man"
dat$gender[dat$gender == "3"] <- "nonbinary"
dat$gender[dat$gender == "4"] <- NA
# maritalStatus
dat$maritalStatus[dat$maritalStatus == "1"] <- "married"
dat$maritalStatus[dat$maritalStatus == "2"] <- "domestic partnership"
dat$maritalStatus[dat$maritalStatus == "3"] <- "single"
dat$maritalStatus[dat$maritalStatus == "4"] <- "divorced or separated"
dat$maritalStatus[dat$maritalStatus == "5"] <- "widowed"
dat$maritalStatus[dat$maritalStatus == "6"] <- NA

# residentialArea
dat$residentialArea[dat$residentialArea == "1"] <- "rural"
dat$residentialArea[dat$residentialArea == "2"] <- "village"
dat$residentialArea[dat$esidentialArea == "3"] <- "urban/city"
dat$residentialArea[dat$residentialArea == "4"] <- "suburban"

# education
dat$education[dat$education == "1"] <- "primary or less"
dat$education[dat$education == "2"] <- "secondary"
dat$education[dat$education == "3"] <- "some teriary"
dat$education[dat$education == "4"] <- "full teritary"
dat$education[dat$education == "5"] <- "graduate degree"

# make sure income is numeric
dat$income <- as.numeric(dat$income)
```
subsets for dataSets split by country:
For this section, I modified the values of the different incomes by converting their income to 2023 USD, after looking up the conversion rate on Google. You might want to get rid of outliers for the specific location tests if you do statistics on them. Maybe we could convert them to what they were at specific year later? 
```{r}
# hong kong (hkd): hongKong
hongKong <- subset(dat, dataSet == "HongKong")
hongKong$income <- (hongKong %>% mutate(income*0.13))$income*0.13


# austria (euros): vienna
vienna <- subset(dat, dataSet == "vienna")
vienna$income <- (vienna %>% mutate(income*1.09))$income*1.09

# canada (cad): toronto, psy202
toronto <- subset(dat, dataSet == "toronto")
toronto$income <- (toronto %>% mutate(income*0.73))$income*0.73
psy202 <- subset(dat, dataSet == "202psy")
psy202$income <- (psy202 %>% mutate(income*0.73))$income*0.73
canada <- rbind(toronto, psy202)

# america: haneda 2019replication, 2018spring, psy250, hatton(?)
spring2018 <- subset(dat, dataSet == "2018spring")
psy250 <- subset(dat, dataSet == "psy250.")
hatton <- subset(dat, dataSet == "hatton")
haneda <- subset(dat, dataSet == "haneda")
replication2019 <- subset(dat, dataSet == "2019replication")
america <- rbind(spring2018, psy250, hatton, haneda, replication2019)
```
full data table
For this section, I removed outliers that made more than 300K or less than 1K
```{r}
full_data_names <- rbind(hongKong, vienna, canada, america)
full_data_names$income[full_data_names$income < 1000 | full_data_names$income > 300000] <- NA
full_data_vals$income <- full_data_names$income
full_data_names <- rbind(hongKong, vienna, canada, america)
full_data_names$income[full_data_names$income < 1000 | full_data_names$income > 300000] <- NA
full_data_vals$income <- full_data_names$income

colnames(dat)[colnames(dat) == "income"] <- "old_income"



#Option 2: Do what Dr Woodward told me to do
 dat$ID <- as.factor(1:nrow(dat))
#
#
 full_data_names$ID <- dat$ID

 a <- select(full_data_names, ID, income)
#
#
# colnames(dat)[colnames(dat) == "income"] <- "old_income"
#
# # should I assign it to result??
dat <- left_join(dat, a, by = "ID")

dat %>% select(income, old_income)

```
statistical tests (for this, use full_data_vals)
```{r}
# some biserial correlation for binary variables
library(ltm)
bsc_smile <- biserial.cor(full_data_vals$income,full_data_vals$smileLaugh, use = "complete.obs")
bsc_enjoyment <- biserial.cor(full_data_vals$income,full_data_vals$enjoyment, use = "complete.obs")
bsc_worry <- biserial.cor(full_data_vals$income,full_data_vals$worry, use = "complete.obs")
bsc_sadness <- biserial.cor(full_data_vals$income,full_data_vals$sadness, use = "complete.obs")
# some pearson product moment correlations
ppm_smile <- cor.test(full_data_vals$income,full_data_vals$smileLaugh)
ppm_enjoyment <- cor.test(full_data_vals$income,full_data_vals$enjoyment)
ppm_worry <- cor.test(full_data_vals$income,full_data_vals$worry)
ppm_sadness <- cor.test(full_data_vals$income,full_data_vals$sadness)
```
graphs (for this, use full_data_names)
```{r}
library(ggplot2)
library(tidyr)
# here is an example of how to make a graph, where NA is not included as a category
full_data_names %>% drop_na(smileLaugh) %>% ggplot(aes(smileLaugh, income)) + geom_boxplot()
```


```{r}
library(ggplot2)
library(tidyr)
# here is an example of how to make a graph, where NA is not included as a category
full_data_names %>% drop_na(smileLaugh) %>% ggplot(aes(smileLaugh, income)) + geom_boxplot()
```

```{r}
dat <- dat %>% mutate(enjoyment= recode(enjoyment, "yes" = "1", "no" = "0"))
dat$enjoyment<- as.numeric(dat$enjoyment)

dat <- dat %>% mutate(smileLaugh= recode(smileLaugh, "yes" = "1", "no" = "0"))
dat$smileLaugh <- as.numeric(dat$smileLaugh)

dat <- dat %>% mutate(sadness= recode(sadness, "yes" = "-1", "no" = "0"))
dat$sadness <- as.numeric(dat$sadness)

dat <- dat %>% mutate(anger= recode(anger, "yes" = "-1", "no" = "0"))
dat$anger <- as.numeric(dat$anger)

dat <- dat %>% mutate(depression= recode(depression, "yes" = "-1", "no" = "0"))
dat$depression <- as.numeric(dat$depression)

dat <- dat %>% mutate(worry= recode(worry, "yes" = "-1", "no" = "0"))
dat$worry <- as.numeric(dat$worry)

dat <- dat %>% mutate(respect= recode(respect, "yes" = "1", "no" = "0"))
dat$respect <- as.numeric(dat$respect)

dat <- dat %>% mutate(learn= recode(learn, "yes" = "1", "no" = "0"))
dat$learn <- as.numeric(dat$learn)

dat <- dat %>% mutate(opportunity= recode(opportunity, "yes" = "1", "no" = "0"))
dat$opportunity <- as.numeric(dat$opportunity)

dat <- dat %>% mutate(livingStandard= recode(opportunity, "yes" = "1", "no" = "0"))
dat$livingStandard <- as.numeric(dat$opportunity)

dat <- dat %>% mutate(emergency= recode(emergency, "yes" = "1", "no" = "0"))
dat$emergency <- as.numeric(dat$emergency)

dat <- dat %>% mutate(time= recode(time, "yes" = "1", "no" = "0"))
dat$time <- as.numeric(dat$time)

dat <- dat %>% mutate(food= recode(food, "yes" = "1", "no" = "0"))
dat$food <- as.numeric(dat$food)

dat <- dat %>% mutate(shelter= recode(shelter, "yes" = "1", "no" = "0"))
dat$shelter <- as.numeric(dat$shelter)

dat <- dat %>% mutate(internetAccess= recode(internetAccess, "yes" = "1", "no" = "0"))
dat$internetAccess <- as.numeric(dat$internetAccess)

dat <- dat %>% mutate(computer= recode(computer, "yes" = "1", "no" = "0"))
dat$computer<- as.numeric(dat$computer)

dat <- dat %>% mutate(television= recode(television, "yes" = "1", "no" = "0"))
dat$television<- as.numeric(dat$television)


# 2. Average smileLaugh and enjoyment into Positive feelings column
dat$PositiveFeelings <- rowMeans(dat[, c("smileLaugh", "enjoyment")], na.rm = TRUE)

# 3. Average worry, sadness, depression, and anger into Negative feelings column
dat$NegativeFeelings <- rowMeans(dat[, c("worry", "sadness", "depression", "anger")], na.rm = TRUE)

# 4. Create another column with logIncome
dat$logIncome <- log(dat$income)

# 5. Create another column of luxury conveniences
dat$LuxuryConveniences <- rowMeans(dat[, c("television", "internetAccess", "computer")], na.rm = TRUE)

# 6. Create another column of basic needs
dat$BasicNeeds <- rowMeans(dat[, c("food", "shelter")], na.rm = TRUE)

# 7. Create another column of psych needs
dat$PsychNeeds <- rowMeans(dat[, c("respect", "learn", "opportunity", "time", "emergency")], na.rm = TRUE)

# 8. Location Names to Numeric
dat[1][dat[1] == "toronto"] <- 1
dat[1][dat[1] == "vienna"] <- 2
dat[1][dat[1] == "2018spring"] <- 3
dat[1][dat[1] == "2019replication"] <- 4
dat[1][dat[1] == "psy250."] <- 5
dat[1][dat[1] == "HongKong"] <- 6
dat[1][dat[1] == "hatton"] <- 7
dat[1][dat[1] == "haneda"] <- 8
dat$dataSet <- as.numeric(dat$dataSet)
dat$dataSet <- factor(dat$dataSet)


class(ladder)
dat$ladder<- as.numeric(dat$ladder)
dat$PositiveFeelings<- as.numeric(dat$PositiveFeelings)
dat$NegativeFeelings<- as.numeric(dat$NegativeFeelings)


allParticipants<-dat #so we don't lose everything you've already done
dat<- na.omit(allParticipants)

model1a <- lm(ladder ~ BasicNeeds + dataSet, data = dat)
model1b <- lm(ladder ~ BasicNeeds + PsychNeeds + dataSet, data = dat)
model1c <- lm(ladder ~ BasicNeeds + PsychNeeds + LuxuryConveniences + livingStandard + dataSet, data = dat)
model1d <- lm(ladder ~ BasicNeeds + PsychNeeds + LuxuryConveniences + livingStandard + logIncome + dataSet, data = dat)


summary(model1a)
summary(model1b)
summary(model1c)
summary(model1d)
 
model2a <- lm(PositiveFeelings ~ BasicNeeds + dataSet, data = dat)
summary(model2a)

model2b <- lm(PositiveFeelings ~ BasicNeeds + PsychNeeds + dataSet, data = dat)
summary(model2b)

model2c <- lm(PositiveFeelings ~ BasicNeeds + PsychNeeds + LuxuryConveniences + livingStandard + dataSet, data = dat)
summary(model2c)

model2d <-lm(PositiveFeelings ~ BasicNeeds + PsychNeeds + LuxuryConveniences + livingStandard + logIncome + dataSet, data = dat)
summary(model2d)
 
 
model3a <- lm(NegativeFeelings ~ BasicNeeds + dataSet, data = dat)
summary(model3a)

model3b <- lm(NegativeFeelings ~ BasicNeeds + PsychNeeds + dataSet, data = dat)
summary(model3b)

model3c <- lm(NegativeFeelings ~ BasicNeeds + PsychNeeds + LuxuryConveniences + livingStandard + dataSet, data = dat)
summary(model3c)

 model3d <-lm(NegativeFeelings ~ BasicNeeds + PsychNeeds + LuxuryConveniences + livingStandard + logIncome + dataSet, data = dat)
summary(model3d)


anova1 <- anova(model1a, model1b, model1c, model1d)
anova1
anova2 <-  anova(model2a, model2b, model2c, model2d)
anova2
anova3 <- anova(model3a, model3b, model3c, model3d)
anova3

```

Graphs
```{r}
library(ggplot2)
library(gridExtra)
#graph of positive feelings ~ Basic Needs
graphDat <- dat
class(graphDat$PositiveFeelings)
class(graphDat$BasicNeeds)
class(graphDat$PsychNeeds)

ggplot(graphDat, aes(PositiveFeelings))+
  geom_histogram(aes(BasicNeeds, fill = "Basic Needs"), binwidth = 0.5, color = "black", alpha = 0.7)+
  geom_histogram(aes(PsychNeeds, fill = "Psychological Needs"), binwidth = 0.5, color = "black", alpha = 0.7)+
  theme_classic()+
  labs(title = "Relationship between Postive Feelings, Psychological Needs, and Basic Needs", 
       y = "Participants", 
       x = "Positive Feelings")+
  scale_fill_manual(values = c("Basic Needs" = "darkgoldenrod3", "Psychological Needs" = "firebrick"), 
                    name = "Variables")

##graphing this another way
ggplot(graphDat, aes(PositiveFeelings, PsychNeeds))+
  geom_jitter(color = "firebrick4")+
  geom_smooth(method = "lm", se = FALSE, color = "black")+
  theme_classic()+
  labs(title = "Relationship between Positive Feelings and Psychological Needs", 
       x = "Positive Feelings", 
       y = "Psychological Needs")

#graph of Income and Positive Feelings
ggplot(graphDat, aes(PositiveFeelings, logIncome))+
  geom_jitter()+
  geom_smooth(method = "lm", se = FALSE, color = "maroon")+
  theme_classic()+
  labs(title = "Relationship between Log Income and Positive Feelings", 
       x = "Positive Feelings", 
       y = "Log Income")

#graph of Negative Feelings and Income
ggplot(graphDat, aes(NegativeFeelings, logIncome))+
  geom_jitter()+
  geom_smooth(method = "lm", se = FALSE, color = "darkgoldenrod3")+
  theme_classic()+
  labs(title = "Relationship between Log Income and Negative Feelings", 
       x = "Negative Feelings", 
       y = "Log Income")

#graph of Positive feelings and luxury items
ggplot(graphDat, aes(PositiveFeelings, LuxuryConveniences))+
  geom_jitter(color = "firebrick4")+
  geom_smooth(method = "lm", se = FALSE, color = "black")+
  theme_classic()+
  labs(title = "Relationship between Positive Feelings and Luxury Conveniences", 
       x = "Positive Feelings", 
       y = "Luxury Conveniences")

```




