---
title: "meta_analysis"
author: "Theodore Rogers, Olivia Costa, Quincey Feragen, Penelope Corbett"
date: "2023-11-21"
output: html_document
---
reading excel spreadsheet
```{r}
library(readxl)
big_data = read_excel("/Users/theodorerogers/Downloads/meta_analysisDat.xlsx")
# do one test on all of the models in table 4
# add study location as predictor
# you don't have to do analyses on specifically one location or another
```
creating dataframe of numerics as default
```{r}
View(big_data)
dat = cbind.data.frame(big_data$dataSet)
# creating dataframe of numerics as default
for (col in big_data[2:28]) {
  dat = cbind.data.frame(dat, as.numeric(col))
}
colnames(dat) <- names(big_data)
```
changing specific values to their specific things (not income, due to currency differences)
```{r}
library(dplyr)
#ladder
ladder <- as.factor(dat$ladder)
dat$ladder <- ladder

# columns 3 to 8
for (i in 3:8) {
  dat[i][dat[i] == "1"] <- "yes"
  dat[i][dat[i] == "2"] <- "no"
}
# columns 11 to 16
for (i in 11:16) {
  dat[i][dat[i] == "1"] <- "yes"
  dat[i][dat[i] == "2"] <- "no"
}
  
# columns 19 to 23
for (i in 19:23) {
  dat[i][dat[i] == "1"] <- "yes"
  dat[i][dat[i] == "2"] <- "no"
}
  
# gender
dat$gender[dat$gender == "1"] <- "woman"
dat$gender[dat$gender == "2"] <- "man"
dat$gender[dat$gender == "3"] <- "nonbinary"
dat$gender[dat$gender == "4"] <- NA

# maritalStatus
dat$maritalStatus[dat$maritalStatus == "1"] <- "married"
dat$maritalStatus[dat$maritalStatus == "2"] <- "domestic partnership"
dat$maritalStatus[dat$maritalStatus == "3"] <- "single"
dat$maritalStatus[dat$maritalStatus == "4"] <- "divorced or separated"
dat$maritalStatus[dat$maritalStatus == "5"] <- "widowed"
dat$maritalStatus[dat$maritalStatus == "6"] <- NA

# residentialArea
dat$residentialArea[dat$residentialArea == "1"] <- "rural"
dat$residentialArea[dat$residentialArea == "2"] <- "village"
dat$residentialArea[dat$esidentialArea == "3"] <- "urban/city"
dat$residentialArea[dat$residentialArea == "4"] <- "suburban"

# education
dat$education[dat$education == "1"] <- "primary or less"
dat$education[dat$education == "2"] <- "secondary"
dat$education[dat$education == "3"] <- "some teriary"
dat$education[dat$education == "4"] <- "full teritary"
dat$education[dat$education == "5"] <- "graduate degree"

# make sure income is numeric
dat$income <- as.numeric(dat$income)
```
subsets for datasets split by country:
For this section, I modified the values of the different incomes by converting their income to 2023 USD, after looking up the conversion rate on Google. Maybe we could convert them to what they were at specific year later?
```{r}
# hong kong (hkd): hongKong
hongKong <- subset(dat, dataSet == "HongKong")
hongKong$income <- (hongKong %>% mutate(income*0.13))$income*0.13

# austria (euros): vienna
vienna <- subset(dat, dataSet == "vienna")
vienna$income <- (vienna %>% mutate(income*1.09))$income*1.09

# canada (cad): toronto, psy202
toronto <- subset(dat, dataSet == "toronto")
toronto$income <- (toronto %>% mutate(income*0.73))$income*0.73
psy202 <- subset(dat, dataSet == "202psy")
psy202$income <- (psy202 %>% mutate(income*0.73))$income*0.73
canada <- rbind(toronto, psy202)

# america: haneda 2019replication, 2018spring, psy250, hatton(?)
spring2018 <- subset(dat, dataSet == "2018spring")
psy250 <- subset(dat, dataSet == "psy250.")
hatton <- subset(dat, dataSet == "hatton")
haneda <- subset(dat, dataSet == "haneda")
replication2019 <- subset(dat, dataSet == "2019replication")
america <- rbind(spring2018, psy250, hatton, replication2019)
```
full data table
```{r}
full_data <- rbind(hongKong, vienna, canada, america)
full_data$income[full_data$income == 0 | full_data$income > 300000] <- NA

```
statistical tests
```{r}

```
graphs
```{r}
library(ggplot2)
ggplot(full_data, aes(smileLaugh, income)) + geom_boxplot()
```
```{r}
#ChatGPT: how to do hierarchical regression

#Pre-analysis:
  #create new column pos feelings with averages of smileLaugh and enjoyment for each individual 
  #this requires a for loop (or mutate?)
#Do the same for negative feelings: worry, sadness, depression, anger
#basic needs unmet: need to average food and shelter
#study sites: need to get a list of all study sites in column dataset
#unique_categories <- unique(my_data$Category)

#dependent_var = Cantril AKA (ladder column) 


# Step 2: Fit a simple linear regression model 

#model 1: Cantril’s Self-Anchoring Striving Scale
model1a <- lm(dependent_var ~ predictor1 + predictor2, data = data)

#Fit a hierarchical regression model, adding study_site as a predictor
model1b <- lm(dependent_var ~ predictor1 + predictor2 + study_site, data = data)


# Step 4: Compare models using ANOVA
anova_result <- anova(model1, modelb)

# Step 5: Display the ANOVA table
print(anova_result)

# Step 6: Check the summary of the final model
summary(model1b)
```

